%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Sales Engineer} % Job title
    {InterSystems - Software Vendor} % Organization
    {Courbevoie, FR, 92} % Location
    {Sep.2014 - PRESENT} % Date(s)
{
InterSystems' \href{https://www.intersystems.com/products/intersystems-iris/}{Data Platform} allows end-users to capture, share, understand and eventually act upon their operational data, in near real-time. Its unified, solid-as-a-rock architecture is a huge step towards success for those of our customers that are facing today's constantly evolving data challenges.
} %Description
{
      \begin{cvitems} % Description(s) of achievements
        \item {Pre-Sales:\\Strategic POC at St Quentin which demonstrate usefulness and rapid deployment of the \href{https://www.intersystems.com/products/healthshare/patient-index/}{HealthShare Enterprise Master Patient Index} solution.\\Involved into the first French sale of \href{https://www.intersystems.com/products/healthshare/patient-index/}{HealthShare Enterprise Master Patient Index}, at Nice's CHU.\\Negotiation and signing of CH Roanne's Enterprise Service Bus service contract.\\Involved in our succesful bid for AFNOR's Enterprise Service Bus.}
        \item {POC \& Demo:\\Supervised learning: succesful POC on islamist tweets classification.\\ \href{https://learning.intersystems.com/pluginfile.php/15024/mod_resource/content/4/AnInterSystemsGuideToTheDataGalaxy.pdf}{Predictive Model integration} into our Data Platform: guessing competitor's incentive to new customers.}
        \item {Post-Sales\\ \href{http://www.hopital-foch.com/hopital/}{Hôpital Foch}(1000 appointments/day) that sits in Suresnes(92) is one of the three members of the \href{http://www.phf.paris/?lang=en}{Paris Hospital Foundation}.\\Upgrade of the \href{https://www.intersystems.com/products/ensemble}{Messages-oriented Middleware}, that is the backbone of the Foch's Information System.\\Deep involving with key users which are typically "very busy at other projects".\\Static code analysis tools development - Evaluate the upgrade complexity and track its progression.\\Refactoring hence non-regression testing and UAT.\\Complete reboot of Ops procedures: automated installation, failover, backup, supervision and Go-Live.\\Implementation of real-time insights.}
      \end{cvitems}
} %Achievements

%---------------------------------------------------------
  \cventry
    {Enterprise Architect} % Job title
    {French Ministry of Finance, Payroll National Operator - End User} % Organization
    {Paris, FR, 75} % Location
    {Sep. 2012 - Aug. 2014} % Date(s)
{
One of the governement's Top 3 projects, with three millions civil servants concerned, Payroll National Operator’s main purpose was to build the new “Fonction publique d’Etat” payroll.
The vision was: offer IaaS to contractors, SaaS to end-users, and eventually chargeback.
I had personal responsibility for our servers infrastructure and was hands-on lead for global IT coherence through normalization, technical coordination and solution design or validation.
} %Description
{
      \begin{cvitems} % Description(s) of achievements
        \item {Datacenter design and organization:\\Worked in close relation with Network, Storage \& System teams.\\Definition of private DNS domain \& sub-domain.\\Blueprint \& technical presentation of machine virtualization project to security officers.}
        \item {Strong support to contractors along solution implementation:\\Horizontal scaling and failover by means of network load balancers.\\SSL endpoints, LDAP directory and SSO, secure communication between servers.\\Application build and deployment: automation, continuous integration, synchronisation of artefacts repository.}
        %\item {Architecure definition and validation:\\Exadata integration in our infrastructure.\\Sizing validation and consolidation (RAM, CPU, HDD, Bandwith), capacity planning.}
        \item {Request For Proposal writing:\\3-year x86 server procurement cycle.\\Relations with Law Department and purchasing service.}
      \end{cvitems}
} %Achievements

%---------------------------------------------------------
  \cventry
    {Application \& Technical Architect} % Job title
    {Bull SAS - System Integrator} % Organization
    {Les Clayes-Sous-Bois, FR, 78} % Location
    {Feb. 2008 - Aug. 2012} % Date(s)
{
I have been involved into a vast range of IT activity from pre-sales to go-live: software integration, Proof of Concept, technical lead on fixed-price software projects, documentation, customer’s project manager interaction.
} %Description
{
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\href{http://www.mediavision.fr}{Mediavision}\\Backoffice App audit by means of code review and static analysis tools.}
        \item {\href{http://www.douane.gouv.fr/articles/a13408-travel-coming-to-france-with-your-pet}{French Customs Intranet}\\Overall design and architecture.\\LDAP-based authentication \& identification.\\Portal mashups: widget \& API / HTML-embedding by means of iframes / browser's new tab.}
        \item {\href{https://www.naval-group.com/en/news/dcns-delivers-multi-mission-frigate-auvergne-the-fourth-fremm-for-the-french-navy/}{Naval Group FREMM}\\Tech Leader for a 7 software engineer team.\\Components’ interfaces definition \& implementation.\\Best practice enforcement: test-driven development, frequent and respectful commit, test suite runs.}
      \end{cvitems}
} %Achievements

%---------------------------------------------------------
  \cventry
    {Application \& Technical Architect} % Job title
    {Atos Integration - System Integrator} % Organization
    {Paris, FR, 75} % Location
    {Feb. 2005 - Jan. 2008} % Date(s)
{
I worked as an engineer then as an architect for Atos, mainly on the design and the implementation on big Java web apps. Examples of such apps are: Agrippa (French weapon owners tracking), Minos (overspeed fines), Cassiopée (French Civil lawcourt processing application)
} %Description
{
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\href{http://www.justice.gouv.fr/template/cache/embeds/embed-2086.html}{Cassiopée}\\Tech Leader for a 8 software engineer team(600 publishing templates delivered).\\Publishing framework conception \& development.\\Unit and integration testing: extensive testing coverage policy; continuous integration (Ant + Junit / DBUnit + Cruise Control).}
        \item {Minos:\\Maintenace and extension of the publishing framework.\\XML schema-based technical specification, POJO marshaling, XML serialization \& transformation.\\Third-party printing tools integration.}
      \end{cvitems}
} %Achievements

%---------------------------------------------------------
  \cventry
    {Software Development Engineer} % Job title
    {EBP - Software Vendor} % Organization
    {Rambouillet, FR, 78} % Location
    {Sep. 2004 - Jan. 2005} % Date(s)
    {\href{https://www.ebp.com}{EBP} is a billing+payroll+accounting specialist with a strong focus on small \& very small businesses.} %Description
{
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Information System Department: global cartography of the overall company's business processes}
        \item {Reboot of the Enterprise’s Knowledge management system:\\Left-pane, Explorer-like, navigation menu.\\Role-based display of items: from public (internet, general documentation) to technical and commercial support (intranet), through various intermediate levels (customer or partner-specific package).}
        \item {Maintenance of the marketing department's Content Managing System.}
      \end{cvitems}
} %Achievements

%---------------------------------------------------------
  \cventry
    {Software Development Engineer} % Job title
    {French Ministry of Sports, FNDS - End User} % Organization
    {Paris, FR, 75} % Location
    {Sep. 2002 - May 2004} % Date(s)
    {FNDS (now \href{http://www.cnds.sports.gouv.fr}{CNDS}) promotes the "sport for all" vision, distributing financial aids to many local, regional and national associations. FNDS' budget was 248 MEUR for year 2004. Recipients logged into the existing public web app and filled in the details about their expenses in relation with the aid they received.} %Description
{
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Data agregation and sharing:\\Extranet conception, development \& deployment (200 users on the whole territory).\\Data reformatting \& uploading towards FNDS local officers's FTP.\\Data aggregation \& HTML reporting towards national officers.\\SQL Server 2000 to Excel \& ACCESS by means of Microsoft's ETL solution Data Transformation Services.\\ASP.NET / IIS, T-SQL, stored procedures.}
        \item {Experts, developers and users coordination.\\Users Documentation \& Teaching.\\User feedback collecting.}
      \end{cvitems}
} %Achievements

%---------------------------------------------------------
  \cventry
    {Software Development Engineer} % Job title
    {The \'Ecole Normale Supérieure, HyperNietzsche - End User} % Organization
    {Paris, FR, 75} % Location
    {Sep. 2001 - Jun. 2002} % Date(s)
{
\href{http://www.nietzschesource.org}{Nietzsche Source} is a publishing web site addressed to researchers in Humanities.
Typical open source project: great remote team (Munich, Pisa, Paris) + innovative ideas implementation + scarce resources.
} %Description
{
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\href{http://www.nietzschesource.org}{Nietzsche Source}:\\Web site architecture, development and maintenance.\\Data access layer: classes’ constructor/destructor by means of view and triggered associated stored procedure.\\Development of online translation module.\\The «html2php» sed program used to transform the Germany-based designers' html pages into php pages.\\Three releases during a 7-months mission.}
      \end{cvitems}
} %Achievements

%---------------------------------------------------------
  \cventry
    {Research \& Teaching Fellow} % Job title
    {Paris 7 Denis Diderot University, Computer Science Dpt} % Organization
    {Paris, FR, 75} % Location
    {Sep. 1996 - Aug. 2001} % Date(s)
    {} %Description
{
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Teaching duties:\\Conception/evaluation of graduating student's final projects: protocol safety \& liveness, race conditions.\\System design \& model checking, database design, Object Oriented Programming.\\C/C++/Java/ORACLE, MAPLE.\\Other specific, model-checking, languages and tools: PROMELA/SPIN, SMV, MEC.}
      \end{cvitems}
} %Achievements

%---------------------------------------------------------
  \cventry
    {Research Fellow} % Job title
    {The Direction Générale de l'Armement, Perception For Robotic Lab} % Organization
    {Montrouge, FR, 92} % Location
    {Sep. 1995 - Aug. 1999} % Date(s)
{
My domain thesis was about using some well known computer science tools (automata, model-checking) into the robotic field. As an example I have defended \href{http://www.aaai.org/Papers/Symposia/Spring/1999/SS-99-05/SS99-05-001.pdf}{this article} at a Stanford University AIII conference.
} %Description
    {} %Achievements

%---------------------------------------------------------
\end{cventries}
