%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Sales Engineer} % Job title
    {InterSystems - Software Vendor} % Organization
    {Courbevoie, FR, 92} % Location
    {Sep.2014 - PRESENT} % Date(s)
{
InterSystems' \href{https://www.intersystems.com/products/intersystems-iris/}{Data Platform} allows its users to capture, share, understand and eventually act upon their operational data, in near real-time. Its unified, solid-as-a-rock architecture is a huge step towards success for those of our customers that are facing today's constantly evolving data challenges.
} %Description
{
      \begin{cvitems} % Description(s) of achievements
        \item {Technical account for \href{http://www.hopital-foch.com/hopital/}{Hôpital Foch}(1000 appointments/day) that sits in Suresnes(92), and is one of the three members of the \href{http://www.phf.paris/?lang=en}{Paris Hospital Foundation}.}
        %\item {Upgrade of the {\href{https://www.intersystems.com/products/ensemble/\#technology}{Messages-oriented Middleware}, that is the backbone of the Foch's Information System.}
        \item {Static code analysis tools development in order to evaluate the upgrade complexity and track its progression, deep involving with key users which are typically "very busy at other projects", massive refactoring hence non-regression testing and UAT, complete reboot of Ops procedures: automated installation, failover, backup, supervision and Go-Live.}
        \item {Implementation of real-time insights (average and standard deviation) on key indicators: number of messages to and from various actors involved into business processes and their associated latencies.}
        \item {Strategic POC at St Quentin which demonstrate usefulness and rapid deployment of the \href{https://www.intersystems.com/products/healthshare/patient-index/}{HealthShare Enterprise Master Patient Index} solution.}
        \item {Involved into the first French sale of \href{https://www.intersystems.com/products/healthshare/patient-index/}{HealthShare Enterprise Master Patient Index}, at Nice's CHU.}
        \item {Supervised learning: succesful POC on islamist tweets classification.}
        \item {Demo on \href{https://learning.intersystems.com/pluginfile.php/15024/mod_resource/content/4/AnInterSystemsGuideToTheDataGalaxy.pdf}{Predictive Model integration} into our Data Platform: guessing competitor's incentive to new customers.}
        \item {Creation of the GitHub's Sales Engineers French repository.}
      \end{cvitems}
} %Achievements

%---------------------------------------------------------
  \cventry
    {Enterprise Architect} % Job title
    {French Ministry of Finance, Payroll National Operator - End User} % Organization
    {Paris, FR, 75} % Location
    {Sep. 2012 - Aug. 2014} % Date(s)
{
Payroll National Operator’s main purpose is to build the new “Fonction publique d’Etat” payroll, its companion BI solution and a Human Resource Information System (HRIS), the latter one being offered “as a service”. As far as three millions civil servants are concerned, it belongs to the Government Modernization's Top 3 projects.
The IT department vision is to offer IaaS to our contractors, SaaS to our end-users, and eventually chargeback.
I had personal responsibility for our servers infrastructure and I must be hands-on lead for global IT coherence through normalization, technical coordination and animation, solution design / validation and datacenter design.
} %Description
{
      \begin{cvitems} % Description(s) of achievements
        \item {Datacenter design and organization, in close relation with Network, Storage \& System teams.}
        \item {Definition of private DNS domain \& sub-domain.}
        \item {Server virtualization project : blueprint \& technical presentation to our security officers.}
        \item {Strong support to contractor while solutions design and implementation : horizontal scaling via network load balancers, failover, SSL endpoints, directory and SSO, secure exchange between servers, application build and deployment (automatisation, continuous integration, synchronisation of artefacts repository).}
        \item {Validation / Definition of project’s architecture (e.g. Exadata integration in our infrastructure).}
        \item {Sizing validation and consolidation (RAM, CPU, HDD, Bandwith), capacity planning.}
        \item {Request For Proposal writing (e.g. our 3-year x86 server procurement cycle), in relation with our Law Dpt and purchasing service.}
      \end{cvitems}
} %Achievements

%---------------------------------------------------------
  \cventry
    {Application \& Technical Architect} % Job title
    {Bull SAS - System Integrator} % Organization
    {Les Clayes-Sous-Bois, FR, 78} % Location
    {Feb. 2008 - Aug. 2012} % Date(s)
{
I have been involved into a vast range of IT activity from pre-sales to go-live: software integration, Proof of Concept, technical lead on fixed-price software projects, documentation, customer’s project manager interaction.
} %Description
{
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {[\href{http://www.mediavision.fr}{Mediavision}] Backoffice App audit by means of code review and static analysis tools.}
        \item {[\href{http://www.douane.gouv.fr/articles/a13408-travel-coming-to-france-with-your-pet}{French Customs Intranet}] Overall design and architecture}
        \item {[\href{http://www.douane.gouv.fr/articles/a13408-travel-coming-to-france-with-your-pet}{French Customs Intranet}] LDAP-based authentication \& identification}
        \item {[\href{http://www.douane.gouv.fr/articles/a13408-travel-coming-to-france-with-your-pet}{French Customs Intranet}] Portal mashups - widget \& API / HTML-embedding by means of iframes / browser's new tab)}
        \item {[\href{https://www.naval-group.com/en/news/dcns-delivers-multi-mission-frigate-auvergne-the-fourth-fremm-for-the-french-navy/}{Naval Group FREMM}]Tech Leader for a 7 software engineer team}
        \item {[\href{https://www.naval-group.com/en/news/dcns-delivers-multi-mission-frigate-auvergne-the-fourth-fremm-for-the-french-navy/}{Naval Group FREMM}]Components’ interfaces definition \& implementation} 
        \item {[\href{https://www.naval-group.com/en/news/dcns-delivers-multi-mission-frigate-auvergne-the-fourth-fremm-for-the-french-navy/}{Naval Group FREMM}]L3-support for conception and development}
        \item {[\href{https://www.naval-group.com/en/news/dcns-delivers-multi-mission-frigate-auvergne-the-fourth-fremm-for-the-french-navy/}{Naval Group FREMM}]Best practice enforcement: test-driven development, frequent and respectful commit, test suite runs, In charge of delivery and its conformity against specifications}
      \end{cvitems}
} %Achievements

%---------------------------------------------------------
  \cventry
    {Application \& Technical Architect} % Job title
    {Atos Integration - System Integrator} % Organization
    {Paris, FR, 75} % Location
    {Feb. 2005 - Jan. 2008} % Date(s)
{
I worked as an engineer then as an architect for Atos, mainly on the design and the implementation on big Java web apps. Examples of such apps are: Agrippa (French weapon owners tracking), Minos (overspeed fines), Cassiopée (French Civil lawcourt processing application)
} %Description
{
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {[\href{http://www.justice.gouv.fr/template/cache/embeds/embed-2086.html}{Cassiopée App}]Tech Leader for a 8 software engineer team.}
        \item {[\href{http://www.justice.gouv.fr/template/cache/embeds/embed-2086.html}{Cassiopée App}]Conception \& development of the Cassiopée's publishing framework.}
        \item {[\href{http://www.justice.gouv.fr/template/cache/embeds/embed-2086.html}{Cassiopée App}]XML schema-based technical specification(about 600 publishing templates); POJO marshaling, XML serialization \& transformation; third-party printing tools integration.}
        \item {[\href{http://www.justice.gouv.fr/template/cache/embeds/embed-2086.html}{Cassiopée App}]Unit and integration testing: extensive testing coverage policy; in charge of continuous integration (Ant + Junit / DBUnit + Cruise Control).}
      \end{cvitems}
} %Achievements

%---------------------------------------------------------
  \cventry
    {Software Development Engineer} % Job title
    {EBP - Software Vendor} % Organization
    {Rambouillet, FR, 78} % Location
    {Sep. 2004 - Jan. 2005} % Date(s)
    {\href{https://www.ebp.com}{EBP} is a billing+payroll+accounting specialist with a strong focus on small \& very small businesses.} %Description
{
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Global cartography of the overall company's business processes}
        \item {Reboot of the Enterprise’s Knowledge management system: left-pane, Explorer-like, navigation menu.}
        \item {Clickable items display was based on authentication levels : from public (internet, general documentation) to technical and commercial support (intranet), through various intermediate levels (customer or partner-specific package).}
        \item {Maintenance of the marketing department's Content Managing System.}
      \end{cvitems}
} %Achievements

%---------------------------------------------------------
  \cventry
    {Software Development Engineer} % Job title
    {French Ministry of Sports, FNDS - End User} % Organization
    {Paris, FR, 75} % Location
    {Sep. 2002 - May 2004} % Date(s)
    {FNDS (now \href{http://www.cnds.sports.gouv.fr}{CNDS}) promotes the "sport for all" vision, distributing financial aids to many local, regional and national associations. FNDS' budget was 248 MEUR for year 2004. Recipients logged into the existing public web app and filled in the details about their expenses in relation with the aid they received.} %Description
{
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Data agregation and sharing: Extranet conception \& development (200 users on the whole territory).}
        \item {Data reformatting \& uploading towards FNDS local officers's FTP - Data Processing from SQL Server 2000 To Excel \& ACCESS by means of Microsoft's ETL solution Data Transformation Services.}
        \item {Data aggregation \& HTML reporting towards national officers - ASP.NET / IIS, T-SQL, stored procedures (SQL Server 2000).}
        \item {Experts, developers and users coordination.}
        \item {Users Documentation \& Teaching - User feedback collecting.}
        \item {In charge of the Extranet's deployment.}
      \end{cvitems}
} %Achievements

%---------------------------------------------------------
  \cventry
    {Software Development Engineer} % Job title
    {The \'Ecole Normale Supérieure, HyperNietzsche - End User} % Organization
    {Paris, FR, 75} % Location
    {Sep. 2001 - Jun. 2002} % Date(s)
{
\href{http://www.nietzschesource.org}{Nietzsche Source} is a publishing web site addressed to researchers in Humanities.
Typical open source project: great remote team (Munich, Pisa, Paris) + innovative ideas implementation + scarce resources.
} %Description
{
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Site architecture. Three releases during a 7-months mission.}
        \item {Data access layer: Classes’ constructor/destructor by means of view and triggered associated stored procedure.}
        \item {The online translation module.}
        \item {An «html2php» sed program used to transform the Germany-based designers' html pages into php pages.}
      \end{cvitems}
} %Achievements

%---------------------------------------------------------
  \cventry
    {Research \& Teaching Fellow} % Job title
    {Paris 7 Denis Diderot University, Computer Science Dpt} % Organization
    {Paris, FR, 75} % Location
    {Sep. 1996 - Aug. 2001} % Date(s)
    {} %Description
{
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Conception/evaluation of graduating student's final projects: protocol safety \& liveness  (nothing bad happens / something good eventually happens), race conditions.}
        \item {Computer science fields that I teached: system design \& model checking, database design, Object Oriented Programming.}
        \item {Computer languages and tools that I teached : C/C++/Java/ORACLE, MAPLE.}
        \item {Other specific, model-checking, languages and tools.}
      \end{cvitems}
} %Achievements

%---------------------------------------------------------
  \cventry
    {Research Fellow} % Job title
    {The Direction Générale de l'Armement, Perception For Robotic Lab} % Organization
    {Montrouge, FR, 92} % Location
    {Sep. 1995 - Aug. 1999} % Date(s)
{
My domain thesis was about using some well known computer science tools (automata, model-checking) into the robotic field. As an example I have defended \href{http://www.aaai.org/Papers/Symposia/Spring/1999/SS-99-05/SS99-05-001.pdf}{this article} at a Stanford University AIII conference.
} %Description
    {} %Achievements

%---------------------------------------------------------
\end{cventries}
